Adolescent well-being in the digital age

### 2022-04-08 02-controls.Rmd
visualize hdi

>>>>

```{r}
hdi <- read_rds("data/hdi.rds")
hdi %>%
  mutate(year = make_date(year)) %>%
  ggplot(aes(year, hdi)) +
  scale_y_continuous(
    "Value",
    labels = ~percent(., .1),
    breaks = pretty_breaks(),
    expand = expansion(.05)
  ) +
  scale_x_date(
    "Year",
    breaks = make_date(c(2005, 2010, 2015, 2020)),
    date_labels = "'%y",
    expand = expansion(.02)
  ) +
  geom_line(
    aes(group = interaction(country)),
    alpha = .25, size = .4, color = "dodgerblue1"
  ) +
  facet_grid(
    ~ region,
    scales = "free_y",
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  theme(
    aspect.ratio = 1,
    legend.position = "none",
    panel.spacing.x = unit(4, "pt"),
    panel.spacing.y = unit(6, "pt"),
    axis.title.y = element_blank()
  )
```

```{r}
# Merge to country-aggregated outcomes
tmp <- dat %>% 
  mutate(year = (year * 10 + 2010)) %>% 
  group_by(country, year, outcome) %>% 
  summarise(val = mean(val, na.rm = TRUE)) %>% 
  ungroup() %>% 
  right_join(hdi) %>% 
  mutate(year = (year - 2010) / 10) %>% 
  drop_na(val)
```
